title TBD

### 2016-01-12 SC-challenge.tex
some work in intro, and added refs

@@

\begin{bottomstuff}
This work is supported by the National Science Foundation, under ...

Some work by D.\ S.\ Katz was supported by the National Science Foundation (NSF) while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.

@@

\section{Introduction}

Software is important in science.

@@

To increase the amount of software developed and shared, we can consider how we might
treat software as if it was a publication.

@@

\section{Related Work}

Ongoing efforts by the WSSSPE Software Credit Working Group and FORCE11 Software Citation Working Group

Codemeta for minimal metadata schemes in JSON and XML

@@

Project CREDiT

\section{Challenges and Research Directions}

key challenges include
\begin{itemize}
\item standardize proper format for citing software in publications, and
\item identify necessary metadata associated with software for citation, 
\item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem.
\end{itemize}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[american]{babel}
\usepackage{textcomp}
\usepackage{csquotes}

\usepackage[breaklinks=true]{hyperref}
\usepackage{url}

@@

\begin{bottomstuff}
Some work by D.\ S.\ Katz was supported by the National Science Foundation (NSF) while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
Some work by K.\ E.\ Niemeyer was supported by the NSF under grant ACI-1535065.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%

Modern science and engineering depend on software. 
However, while traditional research results published in archival journals and conferences can be cited to value the efforts of researchers, no such accepted standard exists to credit the considerable efforts that go into software.

Furthermore, since research results now depend on the specific software used (e.g., version), proper citation---and the associated archiving---is necessary to ensure reproducibility.

@@

To increase the amount of software developed and shared, we can consider how we might
treat software as a publication.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
%%%%%%%%%%%%%%%%%%%%%%%%%

Ongoing efforts by the WSSSPE Software Credit Working Group~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Group

CodeMeta~\cite{CodeMeta} for minimal metadata schemes in JSON and XML

@@

Project CRediT~\cite{project_credit}

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Challenges and Research Directions}
%%%%%%%%%%%%%%%%%%%%%%%%%

Key challenges include
\begin{itemize}
\item standardize proper format for citing software in publications,
\item identify necessary metadata associated with software for citation, 
\item establish mechanism for software to cite other software (i.e., dependencies),
\item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem, and
\item determine role of peer review for software.
\end{itemize}
